Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-01-26 reports/manuscript/supplemental.tex
Capitalize DIPY.
Suggestions and comments on supplement.

\item {\it Diffusion data preprocessing}
Several confounding time-series were calculated based on the
\emph{preprocessed DWI}: framewise displacement (FD) using the
implementation in \emph{Nipype} \cite[following the definitions
by]{power_fd_dvars}. The head-motion estimates calculated in the
correction step were also placed within the corresponding confounds
file. Slicewise cross correlation was also calculated. The DWI
time-series were resampled to ACPC, generating a \emph{preprocessed DWI
run in ACPC space}.
\end{itemize}

Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
\cite[RRID:SCR\_001362]{nilearn} and \emph{Dipy} \cite{dipy}. For more
details of the pipeline, see
\href{https://qsiprep.readthedocs.io/en/latest/workflows.html}{the
section corresponding to workflows in \emph{QSIPrep}'s documentation}.
We will refer to this dataset as HBN.

@@

Data from the HBN and Cam-CAN studies were processed using the updated Python
Automated Fiber Quantification toolbox (\texttt{pyAFQ})\todo{Add pyAFQ
citation}. In addition to demonstrating the our analysis pipeline is robust
to changes in tractometry software, the use of the updated \texttt{pyAFQ}
capitalized upon the following improvements over the legacy Matlab version
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item the ability to ingest data provided in the BIDS format
    \cite{gorgolewski2016brain}
    \item the calculation of diffusion kertosis imaging (DKI
    \cite{jensen2005diffusion}) metrics
\end{enumerate*}
We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
as \texttt{AFQ}.

These processes create bundle profiles, in which diffusion measures
are quantified and averaged along twenty major fiber tracts. Here,
we use only the mean diffusivity (MD) and the fractional anisotropy
(FA) of the diffusion tensor, but additional dMRI-based maps or maps
based on other quantitative MRI measurements can also be used. These
bundle profiles, along with the phenotypical data we wish to explain
or predict, form the input to the SGL algorithm. In a domain-agnostic
machine learning context, the phenotypical data comprise the target
variables while the bundle profiles form the feature or predictor
variables (See \cref{main:fig:methods:group-structure} in the main text).

@@

After scaling and imputation, the tractometry data and target
phenotypical data can be organized in a linear model:
\begin{equation}
    y = \mathbf{X} \beta + \epsilon,
    \label{eq:lm}
\end{equation}
where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
or continuous numerical, such as the subject's age. The tractometry
data is represented in the feature matrix $\mathbf{X}$, with rows
corresponding to different subjects, and columns corresponding
to diffusion measures at different nodes within each bundle. The
relationship between tractometric features and the phenotypic target is
characterized by the coefficients in $\beta$. The error term, $\epsilon$
is an unobserved random variable that captures the error in the model.
We denote our prediction of the targer phenotype as $\hat{y}$ and the
coefficients that produce this prediction as $\hat{\beta}$, so that
\begin{equation}
    \hat{y} = \mathbf{X} \hat{\beta},
    \label{eq:lm-approx}
\end{equation}
without the error term, $\epsilon$. In general, the feature matrix
$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
is the number of subjects, $B$ is the number of white matter bundles,
$N$ is the number of nodes in each bundle, and $M$ is the number of
diffusion metrics calculated at each node. Typically, $B = 20$, $N =
100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 16,000$ features.
Conversely, many dMRI studies have between a few dozen and a few
hundred subjects, yielding a feature matrix that is wide and short.
Even in cases where more than a thousand subjects are measured (e.g.,
in the Human Connectome Project, where 1,200 subjects were measured
\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
of this data requires regularization to avoid overfitting and generate
interpretable results.

Here, we propose that in addition to regularizing the coefficients in
$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
of the bundle profile features in $\mathbf{X}$. The bundle-metric
combinations form a natural grouping. For example, we expect that MD features
within the left arcuate fasciculus will co-vary across individuals. Likewise
for FA values within the right corticospinal tract (CST) and so on. This
group structure is represented in \cref{main:fig:methods:group-structure}, which
depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
regularization approach that will fit a linear model with
anatomically-grouped covariates, where we expect to observe both groupwise
sparsity, where the number of groups (bundle/metric combinations) with at
least one non-zero coefficients is small, as well as within-group sparsity,
where the number of non-zero coefficients within each non-zero group is
small. The sparse group lasso (SGL) is a penalized regression technique that
satisfies exactly these criteria\cite{simon2013sparse}. It solves for a
coefficient vector $\hat{\beta}$ that satisfies
\begin{multline}
    \hat{\beta} = \min_\beta L_{\text{mse}}
    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
    + \alpha \lambda \norm{\beta}_1,\\%
    \text{where} \quad
    L_{\text{mse}} = \frac{1}{2}
    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2
    \label{eq:sgl}
\end{multline}
where $G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
coefficient vector for group $\ell$ and $p_\ell$ is the length of
$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
\ell: p_\ell = 100$. The first term is the mean square error loss,
$L_{\text{mse}}$, as in the standard linear regression framework. The second
and third terms encourage groupwise sparsity and overall sparsity,
respectively. If $\alpha = 1$ the SGL reduces to the traditional
lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
reduces to the group lasso\cite{yuan2006model}. Thus, the model
hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
The hyperparameter $\lambda$ controls the strength of the regularization.

@@

\subsection{Implementation, cross-validation and metaparameter optimization}

@@

Because the SGL is not specific to tractometry, we implement its solution as
a separate Python package called \texttt{groupyr} \cite{groupyr}.
\texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
gradient descent \cite{parikh2014proximal} by implementing a custom proximal
operator and relying on the C-OPT optimization library \cite{copt}, providing
a fitted SGL model as a scikit-learn compatible estimator \cite{sklearn_api}.
\texttt{Groupyr} also selects the hyperparameters $\alpha$ and $\lambda$ that
yield the best cross-validated performance using either
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, or }}]
    \item an exhaustive grid search of hyperparameter combinations
    \item sequential model based optimization using the scikit-optimize
    library \cite{scikit_optimize}.
\end{enumerate*}

To objectively evaluate the model performance and guard against over-fitting,
we used a nested cross-validation scheme, which is depicted for the binary
classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
of the feature matrix $\mathbf{X}$ in \cref{main:fig:methods:group-structure}
and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
hold that fold out as the test\textsubscript{0} set and let the remaining
data comprise the train\textsubscript{0} set, with the subscript indicating
the depth of the nested decomposition. We further decompose each
train\textsubscript{0} set into three folds, and again for each unique fold,
we hold out that fold as the test\textsubscript{1} set and let the remaining
data comprise the train\textsubscript{1} set. At level-1 of the
decomposition, we fit an SGL model using fixed regularization meta-parameters
$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
evaluating the fit on test\textsubscript{1}. We find the optimal values for
$\alpha$ and $\lambda$ using sequential model based optimization, implemented
using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
For continuous numerical $y$, \verb|BayesSearchCV| searches for
meta-parameter values that maximize the $R^2$ averaged over test sets. For
binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
classification accuracy. Using hyperoptimization, we find optimal
regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
set and then use those to predict values for data in test\textsubscript{0}.
Thus each subject in the dataset has a predicted phenotype derived from a
model that never saw its particular subject's data. In the classification
case, the shuffling into folds is stratified such that each fold has a
population that preserves the percentage of each class found in the larger
input data.

@@

The full software implementation of the SGL approach presented here is available
in a Python software package called AFQ-Insight, which is developed publicly in
\url{https://github.com/richford/afq-insight}. The version of the code used to
produce the results herein is also available in
\url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
AFQ-Insight reads the target and feature data that has been processed by AFQ
from comma separated value (CSV) files conforming to the AFQ-Browser data
format \cite{yeatman2018browser} and represents them internally as
\lstinline{DataFrame} objects from the pandas Python library
\cite{mckinney2010data}. The software provides different options for imputing
missing data in the feature matrix. Missing interior nodes are imputed using
linear interpolation. For missing exterior nodes, the user may choose between
linear extrapolation and constant forward(back)-fill. Imputation uses only
values from adjacent nodes in the same white matter bundle in the same
subject so there is no danger of data leakage from other subjects. It uses
the scikit-learn \cite{scikit-learn} library to decompose input data into
separate test and train datasets, to scale each feature to have zero mean and
unit variance, and to evaluate each fit in the hyperparameter search using
appropriate classification and regression metrics such as accuracy, area
under the receiver operating curve (AUC ROC), and coefficient of
determination ($R^2$). For each set of hyperparameters, we solve the SGL
problem using the \texttt{groupyr} library \cite{groupyr}. Appropriate
hyperparameters are found using the scikit-optimize library
\cite{scikit-optimize}.

@@

\Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
coefficients for the ALS dataset FA and MD metrics, respectively. These
figures reinforce the findings in the main text that ALS is localized to the
corticospinal tract. In this study, SGL selected the right corticospinal
tract (CSTR) as important and regularized coefficients in the CSTL. Yet,
\cref{fig:als-bp:fa} also shows group FA differences in the CSTL. This
highlighted a potential drawback of the SGL method, discussed in the main
text in the context of age regression. Namely, SGL is not guaranteed to
identify \emph{all} important features. In this case, if the diagnostic
signal in the CSTL is redundant to that in the CSTR, SGL will regularize the
CSTL features, thereby reducing its sparsity penalty without any
corresponding increase in loss. This parsimony cuts both ways; it is a
feature of the method when one seeks an efficient predictive model, but is a
defect of the method when one wants an exhaustive explanation of feature
importance. We will use the phrase ``parsimonious pitfall'' to refer to the
case when SGL regularizes away redundant but obviously important features.

@@

\Cref{fig:wh-bp:fa,fig:wh-bp:md} show the bundle profiles and regression
coefficients for the WH dataset. In contrast to the ALS classification case,
the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting
the interpretation that aging is a large and continuous whole-brain process.
These figures also show that SGL behaves much more like the lasso than the group
lasso, as discussed in the main text. The parsimonious pitfall is most evident in
the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.

@@

\Cref{fig:hbn-bp:fa,fig:hbn-bp:md} show the bundle profiles and regression
coefficients for the HBN dataset. Like the WH dataset, the $\hat{\beta}$
coefficients are distributed widely through the brain and SGL behaves more
like the lasso than the group lasso. In contrast the the WH results,
the bundle profiles show different behaviors. For example the SLFL and SLFR
bundle profiles in \cref{fig:wh-bp:md} and \cref{fig:hbn-bp:md} have
different concavity. This is unsurprising, however, given the differences
between these datasets
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item different diffusion models, with DTI for the WH dataset and DKI for
    the HBN dataset
    \item different age ranges and distributions (which is evident in the
    figure legends), with HBN being a developmental dataset, while WH is a
    lifespan maturation dataset
    \item different anatomical extents, with the WH streamlines truncated to
    remain with the bundle's bounding regions of interest (the default
    behavior in the legacy \texttt{mAFQ}) and the HBN streamlines allowed
    to retain their full extent from whole-brain tractography (the default
    behavior in \texttt{pyAFQ}).
\end{enumerate*}
Thus, one should use caution when comparing bundle profiles and $\hat{\beta}$
coefficients between the WH, HBN, and Cam-CAN models.
The parsimonious pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:hbn-bp:md}.

@@

\Cref{fig:cc-bp:fa,fig:cc-bp:md} show the bundle profiles and regression
coefficients for the Cam-CAN dataset. Like the WH and HBN datasets, the
$\hat{\beta}$ coefficients are distributed widely through the brain and SGL
behaves more like the lasso than the group lasso. As before, one must be
cautious about comparing bundle profiles and $\hat{\beta}$ coefficients
between models. While the HBN and Cam-CAN datasets share the same diffusion
model and refrain from clipping streamlines, the age distributions for the
two are roughly disjoint, with the WH age distribution straddling the two.
The parsimonious pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:cc-bp:md}.
\todo[inline]{We could say more here but it's not an ``aging'' paper so I
don't really want to. I only want to stress that you have to be careful
comparing $\hat{\beta}$ across models.}

>>>>

\item {\it Diffusion data preprocessing}

\todo{Ariel: This section seems incomplete. I am pretty sure there was some motion correction, eddy current correction and so forth happening in here.
Also, we might want to drop the part that describes calculation of confounds,
since we aren't using them.}

Several confounding time-series were calculated based on the
\emph{preprocessed DWI}: framewise displacement (FD) using the
implementation in \emph{Nipype} following the definitions
by \cite{power_fd_dvars}. The head-motion estimates calculated in the
correction step were also placed within the corresponding confounds
file. Slicewise cross correlation was also calculated. The DWI
time-series were resampled to ACPC, generating a \emph{preprocessed DWI
run in ACPC space}.
\end{itemize}

Many internal operations of \emph{QSIPrep} use \emph{Nilearn} 0.6.2
\cite[RRID:SCR\_001362]{nilearn} and \emph{DIPY} \cite{dipy}. For more
details of the pipeline, see
\href{https://qsiprep.readthedocs.io/en/latest/workflows.html}{the
section corresponding to workflows in \emph{QSIPrep}'s documentation}.
We will refer to this dataset as HBN.

@@

Data from the HBN and Cam-CAN studies were processed using the updated Python
Automated Fiber Quantification toolbox (\texttt{pyAFQ})\todo{Add pyAFQ
citation}. In addition to demonstrating the our analysis pipeline is robust
to changes in tractometry software, the use of the updated \texttt{pyAFQ}
capitalized upon the following improvements over the legacy Matlab version
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item the ability to ingest data provided in the BIDS format
    \cite{gorgolewski2016brain}
    \item the calculation of diffusion kurtosis imaging (DKI
    \cite{jensen2005diffusion}) metrics
\end{enumerate*}
We will refer to the \texttt{mAFQ} and \texttt{pyAFQ} pipeline collectively
as \texttt{AFQ}.

These processes create bundle profiles, in which diffusion measures
are quantified and averaged along eighteen major fiber tracts. Here,
we use only the mean diffusivity (MD) and the fractional anisotropy
(FA) of the diffusion tensor, but additional dMRI-based maps or maps
based on other quantitative MRI measurements can also be used. These
bundle profiles, along with the phenotypical data we wish to explain
or predict, form the input to the SGL algorithm. In a domain-agnostic
machine learning context, the phenotypical data comprise the target
variables while the bundle profiles form the feature or predictor
variables (See \cref{main:fig:methods:group-structure} in the main text).

@@

After scaling and imputation, the tractometry data and target
phenotypical data can be organized in a linear model:
\begin{equation}
    y = \mathbf{X} \beta + \epsilon,
    \label{eq:lm}
\end{equation}
where $y$ is the phenotype -- categorical, such as a clinical diagnosis,
or continuous numerical, such as the subject's age. The tractometry
data is represented in the feature matrix $\mathbf{X}$, with rows
corresponding to different subjects, and columns corresponding
to diffusion measures at different nodes within each bundle. The
relationship between tractometric features and the phenotypic target is
characterized by the coefficients in $\beta$. The error term, $\epsilon$
is an unobserved random variable that captures the error in the model.
We denote our prediction of the target phenotype as $\hat{y}$ and the
coefficients that produce this prediction as $\hat{\beta}$, so that
\begin{equation}
    \hat{y} = \mathbf{X} \hat{\beta},
    \label{eq:lm-approx}
\end{equation}
without the error term, $\epsilon$. In general, the feature matrix
$\mathbf{X}$ has dimensions $S \times (B \times N \times M)$, where $S$
is the number of subjects, $B$ is the number of white matter bundles,
$N$ is the number of nodes in each bundle, and $M$ is the number of
diffusion metrics calculated at each node. Typically, $B = 18$, $N =
100$, and $2 \le M \le 8$, resulting in $\sim 4,000 - 14,400$ features.
Conversely, many dMRI studies have between a few dozen and a few
hundred subjects, yielding a feature matrix that is wide and short.
Even in cases where more than a thousand subjects are measured (e.g.,
in the Human Connectome Project, where 1,200 subjects were measured
\cite{VanEssen2012}), the problem is ill-posed: the high dimensionality
of this data requires regularization to avoid overfitting and generate
interpretable results.

Here, we propose that in addition to regularizing the coefficients in
$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
of the bundle profile features in $\mathbf{X}$. The bundle-metric
combinations form a natural grouping. For example, we expect that MD features
within the left arcuate fasciculus will co-vary across individuals. Likewise
for FA values within the right corticospinal tract (CST) and so on. This
group structure is represented in \cref{main:fig:methods:group-structure}, which
depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
regularization approach that will fit a linear model with
anatomically-grouped covariates, where we expect to observe both groupwise
sparsity, where the number of groups (bundle/metric combinations) with at
least one non-zero coefficients is small, as well as within-group sparsity,
where the number of non-zero coefficients within each non-zero group is
small. The sparse group lasso (SGL) is a penalized regression technique that
satisfies these criteria\cite{simon2013sparse}. It solves for a
coefficient vector $\hat{\beta}$ that satisfies
\begin{multline}
    \hat{\beta} = \min_\beta L_{\text{mse}}
    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
    + \alpha \lambda \norm{\beta}_1,\\%
    \text{where} \quad
    L_{\text{mse}} = \frac{1}{2}
    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2,
    \label{eq:sgl}
\end{multline}
$G$ is the number of groups $\mathbf{X}^{(\ell)}$ is the submatrix of
$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
coefficient vector for group $\ell$ and $p_\ell$ is the length of
$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
\ell: p_\ell = 100$. The first term is the mean square error loss,
$L_{\text{mse}}$, as in the standard linear regression framework. The second
and third terms encourage groupwise sparsity and overall sparsity,
respectively. If $\alpha = 1$ the SGL reduces to the traditional
lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
reduces to the group lasso\cite{yuan2006model}. Thus, the model
hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
The hyperparameter $\lambda$ controls the strength of the regularization.

@@

\subsection{SGL implementation, cross-validation and metaparameter optimization}

@@

Because the SGL is not specific to tractometry, we implemented its solution as
a general-purpose Python package called \texttt{groupyr} \cite{groupyr}.
\texttt{Groupyr} solves the cost function in \cref{eq:sgl} using proximal
gradient descent \cite{parikh2014proximal} by implementing a custom proximal
operator and relying on the C-OPT optimization library \cite{copt}, providing
a fitted SGL model as a scikit-learn compatible estimator \cite{sklearn_api}.
\texttt{Groupyr} also selects the hyperparameters $\alpha$ and $\lambda$ that
yield the best cross-validated performance using either
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, or }}]
    \item an exhaustive grid search of hyperparameter combinations
    \item sequential model based optimization using the scikit-optimize
    library \cite{scikit_optimize}.
\end{enumerate*}

To objectively evaluate model performance and guard against over-fitting,
we used a nested cross-validation scheme, which is depicted for the binary
classification case in \cref{fig:nested-cross-val}. The subjects (i.e. rows
of the feature matrix $\mathbf{X}$ in \cref{main:fig:methods:group-structure}
and \cref{eq:lm}) are first shuffled and then decomposed into $k_0$ batches,
hereafter referred to as folds. For the ALS and WH datasets, we used $k_0 =
10$ and for the HBN and Cam-CAN datasets, $k_0 = 5$. For each unique fold, we
hold that fold out as the test\textsubscript{0} set and let the remaining
data comprise the train\textsubscript{0} set, with the subscript indicating
the depth of the nested decomposition. We further decompose each
train\textsubscript{0} set into three folds, and again for each unique fold,
we hold out that fold as the test\textsubscript{1} set and let the remaining
data comprise the train\textsubscript{1} set. At level-1 of the
decomposition, we fit an SGL model using fixed regularization meta-parameters
$\alpha$ and $\lambda$, training the model using train\textsubscript{1} and
evaluating the fit on test\textsubscript{1}. We find the optimal values for
$\alpha$ and $\lambda$ using sequential model-based optimization, implemented
using the scikit-optimize \verb|BayesSearchCV| class\cite{scikit-optimize}.
For continuous numerical $y$, \verb|BayesSearchCV| searches for
meta-parameter values that maximize the $R^2$ averaged over test sets. For
binary categorical $y$ \verb|BayesSearchCV| seeks to maximize the
classification accuracy. Using hyperoptimization, we find optimal
regularization parameters and $\hat{\beta}$ for each train\textsubscript{0}
set and then use those to predict values for data in test\textsubscript{0}.
Thus each subject in the dataset has a predicted phenotype derived from a
model that never saw its particular subject's data. In the classification
case, the shuffling into folds is stratified such that each fold has a
population that preserves the percentage of each class found in the larger
input data.

@@

The full software implementation of the SGL approach presented here is available
in a Python software package called \texttt{AFQ-Insight}, which is developed
publicly in \url{https://github.com/richford/afq-insight}.
The version of the code used to produce the results herein is also available in
\url{https://doi.org/10.5281/zenodo.3585942}\todo{Update version here}.
AFQ-Insight reads the target and feature data that has been processed by AFQ
from comma separated value (CSV) files conforming to the AFQ-Browser data
format \cite{yeatman2018browser} and represents them internally as
\lstinline{DataFrame} objects from the pandas Python library
\cite{mckinney2010data}. The software provides different options for imputing
missing data in the feature matrix. Missing interior nodes are imputed using
linear interpolation. For missing exterior nodes, the user may choose between
linear extrapolation and constant forward- or back-fill. Imputation uses only
values from adjacent nodes in the same white matter bundle in the same
subject so there is no danger of data leakage from other subjects. It uses
the scikit-learn \cite{scikit-learn} library to decompose input data into
separate test and train datasets, to scale each feature to have zero mean and
unit variance, and to evaluate each fit in the hyperparameter search using
appropriate classification and regression metrics such as accuracy, area
under the receiver operating curve (AUC ROC), and coefficient of
determination ($R^2$). Internally, \texttt{AFQ-Insight} uses the \texttt{groupyr} software library \cite{groupyr} mentioned above to solve the SGL.

@@

\Cref{fig:als-bp:fa,fig:als-bp:md} show the bundle profiles and regression
coefficients for the ALS dataset FA and MD metrics, respectively. These
figures reinforce the findings in the main text that ALS is localized to the
corticospinal tract. In this study, SGL selected the right corticospinal
tract (CSTR) as important and regularized coefficients in the CSTL. Yet,
\cref{fig:als-bp:fa} also shows group FA differences in the CSTL. This
highlighted a potential drawback of the SGL method, discussed in the main
text in the context of age regression. Namely, SGL is not guaranteed to
identify \emph{all} important features. In this case, if the diagnostic
signal in the CSTL is redundant to that in the CSTR, SGL will regularize the
CSTL features, thereby reducing its sparsity penalty without any
corresponding increase in loss. This parsimony cuts both ways; it is a
feature of the method when one seeks an efficient predictive model, but is a
disadvantage of the method when one wants an exhaustive explanation of feature
importance. We will use the phrase ``parsimony pitfall'' to refer to the
case when SGL regularizes away redundant but obviously important features.

@@

\Cref{fig:wh-bp:fa,fig:wh-bp:md} show the bundle profiles and regression
coefficients for the WH dataset. In contrast to the ALS classification case,
the $\hat{\beta}$ coefficients are distributed widely through the brain, supporting
the interpretation that aging is a large and continuous whole-brain process.
These figures also show that SGL behaves much more like the lasso than the group
lasso, as discussed in the main text. The parsimony pitfall is most evident in
the IFOL and IFOR bundles in \cref{fig:wh-bp:md}.

@@

\Cref{fig:hbn-bp:fa,fig:hbn-bp:md} show the bundle profiles and regression
coefficients for the HBN dataset. Like the WH dataset, the $\hat{\beta}$
coefficients are distributed widely through the brain and SGL behaves more
like the lasso than the group lasso. In contrast the the WH results,
the bundle profiles show different behaviors. For example the SLFL and SLFR
bundle profiles in \cref{fig:wh-bp:md} and \cref{fig:hbn-bp:md} have
different concavity. This is unsurprising, however, given the differences
between these datasets
\begin{enumerate*}[%
    label=(\roman*),%
    before=\unskip{: },%
    itemjoin={{, }},%
    itemjoin*={{, and }}]
    \item different diffusion models, with DTI for the WH dataset and DKI for
    the HBN dataset
    \item different age ranges and distributions (which is evident in the
    figure legends), with HBN being a developmental dataset, while WH is a
    lifespan maturation dataset
    \item different anatomical extents, with the WH streamlines truncated to
    remain with the bundle's bounding regions of interest (the default
    behavior in the legacy \texttt{mAFQ}) and the HBN streamlines allowed
    to retain their full extent from whole-brain tractography (the default
    behavior in \texttt{pyAFQ}).
\end{enumerate*}
Thus, one should use caution when comparing bundle profiles and $\hat{\beta}$
coefficients between the WH, HBN, and Cam-CAN models.
The parsimony pitfall is most evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:hbn-bp:md}.

@@

\Cref{fig:cc-bp:fa,fig:cc-bp:md} show the bundle profiles and regression
coefficients for the Cam-CAN dataset. Like the WH and HBN datasets, the
$\hat{\beta}$ coefficients are distributed widely through the brain and SGL
behaves more like the lasso than the group lasso. As before, one must be
cautious about comparing bundle profiles and $\hat{\beta}$ coefficients
between models. While the HBN and Cam-CAN datasets share the same diffusion
model and refrain from clipping streamlines, the age distributions for the
two are roughly disjoint, with the WH age distribution straddling the two.
The parsimony pitfall is again evident in the UNCL, UNCR, ARCL, SLFL, and
SLFR bundles in \cref{fig:cc-bp:md}.
\todo[inline]{We could say more here but it's not an ``aging'' paper so I
don't really want to. I only want to stress that you have to be careful
comparing $\hat{\beta}$ across models. Ariel: agreed!}
